---
output:
  md_document:
    variant: markdown_github
---


```{r, setup, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  fig.path = "man/figures/"
)
```

Overview
------------

`pearsonverse` is a set of packages which facilitates the data science process in R. The __pearsonverse__ package is designed to make it easy to install and load core packages from the pearsonverse in a single command.


Installation
------------

```{r, warning = F, eval = F}
devtools::install_github("pearsonplc/pearsonverse")
```

Usage
------------

`library(pearsonverse)` will load the core `pearsonverse` packages:

-  <a href = "https://github.com/pearsonplc/skelpear" target = "_blank">skelpear</a>, for building a project environment and maintaining a reproducibility.
-  <a href = "https://github.com/pearsonplc/reppear" target = "_blank">reppear</a>, for building a reproducible report with standardised layout.
-  <a href = "https://github.com/pearsonplc/vispear" target = "_blank">vispear</a>, for creating visualisation with coherent layout.

You also get a condensed summary when you have loaded:

```{r}
library(pearsonverse)
```

__Data Science Workflow__

1.&nbsp;Attach all pearson packages

```{r,eval=F}
library(pearsonverse)
```

2.&nbsp;Create a new project. It will open a new session.

```{r,eval=F}
skelpear::project_create(project_name = "example_project")
```

3.&nbsp;In the console, the warning shows up:

```{r,eval=F}
"Warning: There is no `packages.dcf` file in your project. 
Please use `snapshot_pkg` function to save your package environment."
```

The `packages.dcf` file lists all attached packages used during the project. It is especially useful when there are more people involved in a code development and when identical package environment is critical.

4.&nbsp;Save your package environment.

```{r,eval=F}
skelpear::snapshot_pkg()
```

The function will save your package environment in `config/packages.dcf` file. Once you push it to the bitbucket repository, anybody can pull it and compare to the local package envrionment via `compare_snapshot` function. You can find more info about these functions in  <a href = "https://github.com/pearsonplc/skelpear" target = "_blank">skelpear</a> package introduction.

5.&nbsp;Then you can start producing code.
6.&nbsp;Once you're ready to prepare a report with your analysis, use `report_create` function

7.&nbsp;Initialize report environment
```{r,eval=F}
reppear::report_create(file = "01_report")
```

By default, the report environment will be stored in `reports` directory. More info about the structure of report directory  <a href = "https://github.com/pearsonplc/reppear" target = "_blank">here</a>.

8.&nbsp;Once you finalised your report, prepare `index.Rmd` file which acts as home page for your report/s.

9.&nbsp;Render all files in `report` directory.

```{r,eval=F}
reppear::render_all()
```

10.&nbsp;Then you're ready to publish the whole `reports` directory on your server.

```{r,eval=F}
reppear::publish()
```
